Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-07 draft.tex
small additions

\begin{document}
\title{Centralizers of higher enveloping algebras of Lie algebras}

@@

First, recall that an $L_\infty$ algebra $\fg$, with its collection of brackets $\{\ell_n\}_{n \geq 1}$ is fully encoded by its dg conilpotent cocommutative coalgebra
\[
\cliels(\fg) = \bigg(\Sym(\fg[1]) \; , \; \d = \sum_{n \geq 1} \ell_n\bigg)
\]
where the sum of the brackets provides a square-zero coderivation.
The square-zero condition efficiently encodes the higher Jacobi relations.
This coalgebra is canonically coaugmented by the inclusion of the base field $k \xto{\simeq} \Sym^0(\fg[1])$.
There is thus a subcoalgebra $\overline{\cliels(\fg)} \subset \cliels(\fg)$ given by the direct sum over positive symmetric powers of $\fg[1]$,
which can be identified with both the kernel of the counit map as well as cokernel of the coaugmentation map.
In short,
\[
\cliels(\fg) = k \oplus \overline{\cliels(\fg)}
\]
as complexes.

@@

@@

Recall from Section~\ref{sec: review of linfty} the natural decomposition 
\[
\clies(\fg,(\cliels(\fh)_f)) \cong k \oplus \Hom^\bullet(\overline{\cliels(\fg)}, \cliels(\fh)_f)
\]
and that the summand $k$ encodes the defining map~$f: \fg \rightsquigarrow \fh$.
(Abusively, here $f$, $\fg$, and $\fh$ denote generic elements and not those appearing in the theorem we are proving.)
Hence, any element $\varphi$ in $\bZ_n(f)$, for instance, has the form
\[
\varphi =\lambda_\varphi \mathbf{1} +\overline{\varphi}
\]
where $\lambda_\varphi \in k$, encoding the component in the first summand, and $\overline{\varphi}$ denotes the component in the second summand.

\begin{dfn}\label{def:comp}
For any \emph{connected} open set $W$, we define the composition 
\[
\bZ_n(g)(W) \otimes \bZ_n(f)(W) \xto{(-\star-)} \bZ_n(g \circ f)(W)
\]
as follows.
For any element
\[
\psi=\lambda_\psi \mathbf{1} +\overline{\psi} \in \bZ_n(g)(W) = \clies(\fh \otimes \Omega(W), \bU_n \fl (W)  )
\]
and any element
\[
\varphi =\lambda_\varphi \mathbf{1} +\overline{\varphi}\in \bZ_n(f)(W) = \clies(\fg \otimes \Omega(W), \bU_n \fh (W)  ),
\] 
set
\[
\psi \star \varphi =  \lambda_{\psi} \lambda_{\varphi} \mathbf{1}+
\lambda_\psi g\circ \overline{\varphi} + \lambda_{\varphi} \overline{\psi} \circ \iota_W \circ f +\overline{\psi} \circ \iota_W \circ \overline{\varphi} 
\]
where $\iota_W$ denotes the inclusion $\Omega^*_c(W) \hookrightarrow \Omega^*(W)$ extended in the obvious way to this setting.
\end{dfn}

>>>>

\begin{document}
\title{Centers and centralizers of higher enveloping algebras of Lie algebras}

@@

First, recall that an $L_\infty$ algebra $\fg$, with its collection of brackets $\{\ell_n\}_{n \geq 1}$ is fully encoded by its dg conilpotent cocommutative coalgebra
\[
\cliels(\fg) = \bigg(\Sym(\fg[1]) \; , \; \d = \sum_{n \geq 1} \ell_n\bigg)
\]
where the sum of the brackets provides a square-zero coderivation.
The square-zero condition efficiently encodes the higher Jacobi relations.
We call $\cliels(\fg)$ the {\em Lie algebra chains} (or Chevalley-Eilenberg chains) of~$\fg$.

This coalgebra is canonically coaugmented by the inclusion of the base field $k \xto{\simeq} \Sym^0(\fg[1])$.
There is thus a subcoalgebra $\overline{\cliels(\fg)} \subset \cliels(\fg)$ given by the direct sum over positive symmetric powers of $\fg[1]$,
which can be identified with both the kernel of the counit map as well as cokernel of the coaugmentation map.
In short,
\[
\cliels(\fg) = k \oplus \overline{\cliels(\fg)}
\]
as complexes.

This construction is symmetric monoidal.
The {\em product} of two $L_\infty$ algebras $\fg \times \fh$ is the direct sum of the underlying graded vector spaces $\fg \oplus \fh$ equipped with the brackets encoded by the tensor product of their chains
\[
\cliels(\fg \times \fh) = \cliels(\fg) \otimes \cliels(\fh),
\]
which piggybacks on the fact that $\Sym$ is a symmetric monoidal functor.

@@

\owen{The weird and interesting bit is to compute the factorization homology over a nontrivial (closed) manifold.}

@@

Recall from Section~\ref{sec: review of linfty} the natural decomposition 
\[
\clies(\fg,(\cliels(\fh)_f)) \cong k \oplus \Hom^\bullet(\overline{\cliels(\fg)}, \cliels(\fh)_f)
\]
and that the summand $k$ corresponds to (scalar multiples of) the defining map~$f: \fg \rightsquigarrow \fh$.
(Abusively, here $f$, $\fg$, and $\fh$ are generic and are not those appearing in the theorem we are proving here.)
Hence, any element $\varphi$ in $\bZ_n(f)$, for instance, has the form
\[
\varphi =\lambda_\varphi \mathbf{1} +\overline{\varphi}
\]
where $\lambda_\varphi \in k$, encoding the component in the first summand, and $\overline{\varphi}$ denotes the component in the second summand.

\begin{dfn}\label{def:comp}
For any \emph{connected} open set $W$, we define the composition 
\[
\bZ_n(g)(W) \otimes \bZ_n(f)(W) \xto{(-\star-)} \bZ_n(g \circ f)(W)
\]
as follows.
For any element
\[
\psi=\lambda_\psi \mathbf{1} +\overline{\psi} \in \bZ_n(g)(W) = \clies(\fh \otimes \Omega(W), \bU_n \fl (W)  )
\]
and any element
\[
\varphi =\lambda_\varphi \mathbf{1} +\overline{\varphi}\in \bZ_n(f)(W) = \clies(\fg \otimes \Omega(W), \bU_n \fh (W)  ),
\] 
set
\[
\psi \star \varphi =  \lambda_{\psi} \lambda_{\varphi} \mathbf{1}+
\lambda_\psi g\circ \overline{\varphi} + \lambda_{\varphi} \overline{\psi} \circ \iota_W \circ f +\overline{\psi} \circ \iota_W \circ \overline{\varphi} 
\]
where the inclusion $\iota_W: \Omega^*_c(W) \hookrightarrow \Omega^*(W)$ is extended in the obvious, functorial way to this setting.
\end{dfn}
